Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-09 Ben_Manuscripts/structure_paper/Draft.tex
Minor edits
New figures

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will in theory 
  converge to a single equilibrium configuration, but that time is far beyond the 100's of 
  nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
  and disordered basins. What we find is that any system where $\mathit{d}=3.7$ \AA~can generally 
  be characterized as being in an
  more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can be characterized as a more the disordered basin.
  Generally, when monomers are started further apart, they stay further apart than systems where
  monomers are started closer together (see Table~\ref{table:correlation_length}). Because of the
  extra space between stacked monomers, monomer head groups have more rotational freedom. We
  quantified the ordering of the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order} for details of calculation). 
  Disordered basin systems have a lower nematic order parameter (meaning they are more disordered) 
  than ordered basin systems.

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that
  is most consistent with the experimental value of 4.12 nm derived from SAXS
  measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
  columns per pore equilibrate to an average pore spacing 0.25 nm lower than
  experiment. Ordered basin systems built with 6 columns per pore, have an
  equilibrated pore spacing ca. 0.50 nm higher than experiment.  Monomers in
  disordered basin systems built with 6 columns-per-pore agree with experimental
  pore-to-pore distances within error, but stack too far apart. Those in the
  disordered sandwiched and disordered parallel displaced configurations stack
  $\sim$4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA further apart
  than suggested by experiment. 5 column-per-pore systems stack, at a maximum,
  0.9 \AA~further apart than experiment (see 
  Table~\ref{table:correlation_length}).  The remainder of this discussion will
  focus on the analysis of systems built with 5 columns per pore.

@@

  The simulated XRD patterns of the parallel displaced configurations show an additional
  reflection due to their helical structure. There are weak horizontal reflections near $|q_z|= 
  0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$. The reflection does not cross through
  $q_r = 0~\AA^{-1}$ so it does not necessarily appear for the same reason as R-double. 
  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
  head groups in the parallel displaced configuration are arranged in a helix.
  It is possible that these reflections contribute to the diffuse reflections that connect
  R-spots and R-double in the experimental pattern.

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
  agrees with experiment. There is no R-double intensity to be measured. Figures
  are provided in section S-\ref{S-section:xrd_intensities} to make these measurements clear.

@@

  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  R-spots originates from the monomer tails. By removing all non-tail atoms from 
  the trajectory and simulating a diffraction pattern with the remaining atoms, 
  we were able to isolate the cause of the spots to the tails 
  (Figure~\ref{fig:tails_rzplot}).

  The tails pack together hexagonally. We plotted the center of mass of the 
  first four tail atoms of each tail originating from each head group 
  (Figure \ref{fig:centroids}). We measured the angle between each center of
  mass and its nearest neighbors with respect to the $xy$ plane of the membrane. 
  We see distinct peaks in the distribution of these angles located ca. 
  $-60\degree$, $0\degree$, and $60\degree$ which is consistent with a 
  hexagonally packed configuration (Figure~\ref{fig:layered_tails}). This 
  ordering dies off at the tail ends, where there is more space to fill 
  causing them to pack nearly isotropically (See supporting information).

@@

  % BJC9: This still needs to be worked out. Rest of section should still hold up
  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
  experimental data is best fit with a Lorentzian function while the simulated
  patterns are best fit using a Gaussian function. The simulated spectra do not
  incorporate the effects of finite domain sizes, pressure broadening and
  instrumental broadening which would alter the peak shape. In the absence of
  these and other peak broadening effects, the experimental peak would actually
  be narrower, further increasing the discrepancy with simulation.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.194 $\pm$ 0.013 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.962 $\pm$ 0.010 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \caption{
  In experiments ((a) and (b)), (a), R-$\pi$ broadens in the $q_z$ direction
  with a FWHM of 0.110 $\pm$ 0.003 $\AA^{-1}$ when fit with a Lorentzian
  function. (b) R-$\pi$ broadens in the $q_r$ direction with a FWHM of 0.792
  $\pm$ 0.009 $\AA^{-1}$ when fit with a Lorentzian function. In our simulations
  ((c) and (d)), (c) the FWHM of R-$\pi$ in the $q_z$ direction is 0.194 $\pm$
  0.013 $\AA^{-1}$ when fit with a Gaussian function, nearly twice the width of
  experiment. (d) The simulated FWHM in the $q_r$ direction is 0.962 $\pm$ 0.01
  $\AA^{-1}$ when fit with a Gaussian function, about 20 \% larger than
  experiment. Note that the large spike in the center is not included in the
  fit.}\label{fig:rpi_exp_comparison}
  \end{figure}

  We have identified a number of potential ways that simulation conditions,
  forcefield and initial configurations could affect the intensity and shape of
  R-$\pi$. We assessed each using a
  simplified model. Our simplified model represents each monomer head group as a
  single point and places them in either a parallel displaced or sandwiched
  configuration. We chose to explore the influence of thermal noise in each
  dimension, the effect of $z$-direction distance correlations between scatterers
  within columns, as well as correlation between columns since these are the
  variables we believe have the largest influence on peak shape and intensity.
  %MRS9: probably best to focus on the variables that we think could cause a problem (i.e. hypotheses to test) first, then talk about how the experiments tested these hypotheses.

  As a baseline, we created a simplified model using the same amount of
  disorder present in our atomistic simulations. There are two sources of
  disorder to consider: thermal motion of atoms and quenched disorder which is
  created by rapid structural rearrangement during early equilibration and is
  largely locked into place for the remainder of the simulation. The latter has
  important implications for the reproducibility of this work since both initial
  configurations and initial velocity randomization can
  lead to different quenched configurations. We measured thermal disorder by
  calculating the standard deviation of the distribution of head group center of
  mass positions from their average positions. We measured quenched disorder by
  calculating the standard deviation of the distribution of head group center of
  masses from their idealized average positions. In the $z$-direction, we
  measured the deviation of the head group center of masses from an equally
  spaced column of head groups. In the $xy$ plane, we calculated the deviation in
  radial position from the pore center and the angular deviation from equally
  spaced points surrounding the pore center. This method for calculating 
  quenched order inherently includes thermal disorder. The values measured for
  each system and type of disorder are given in Table~\ref{table:quenched_disorder}.

  The intensity of R-$\pi$ can be calculated from a single trajectory of
  uncorrelated configurations rather than from the average of multiple correlated
  trajectories. Theoretically, in order to mimic the simulated system, we should
  build an initial configuration which has the same amount of quenched disorder
  as our simulations and then create a trajectory to which we add thermal
  noise to each subsequent frame. In this scenario, the positions of each scatterer
  will not change in a way that significantly affects the intensity of R-$\pi$
  since most of its character is defined by the far more disordered initial configuration.
  To uncover the expected intensity of R-$\pi$, we would need to average over many
  such trajectories. To bypass this expensive calculation, we instead calculate the
  R-$\pi$ intensity from a trajectory consisting of many independent initial 
  configurations. This simulates the long time scales over which we expect columns
  to sample many configurational states. %We use the latter method for the remainder of
%  this section since we can extract the trends we need using a single trajectory at
%  a fraction of the computational cost.

 %BJC9 : Could show some number like the following
%  The average R-$\pi$ intensity of 40, 100 frame trajectories created in this (1st way mentioned above)
%  way was 16.0 $\pm$ 4.9. If instead we create a single trajectory from 1000
% initial configurations, the intensity of R-$\pi$ is 16.42, in close agreement
%  with the mean of 40 simulations.

@@

  The correlation length of vertically stacked scatterers in our simulations
  are in reasonable agreement with experiment. Since it is not feasible for us to
  simulate membranes with much taller columns for increased $q_z$ resolution, and
  because the peak shape is convoluted by the extremely intense maximum of
  R-$\pi$, we measured correlation length by plotting the one-dimensional pair
  distribution function, $g(z)$, for the centers of mass of monomer phenyl rings
  (Figure~\ref{fig:correlation}). 
  %We used this 
  %information to understand how far apart monomers stack within monomer columns and
  %the degree to which they are correlated.

@@

  The correlation length of the parallel displaced, ordered basin system shows
  the closest agreement with experiment (Table~\ref{table:correlation_length}).
  We calculated the correlation length of each system using
  Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable
  correlation length from the disordered parallel displaced configuration since
  the peaks do not show clear patterns that can easily be fit to an exponential
  decay. The correlation length of both sandwiched systems is relatively low
  because the height of the first peak of $g(z)$ is so high.

@@

  Increased thermal noise in the $z$-direction causes a drop in the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
  thermal noise of our parallel displaced simple system in the $z$-direction by
  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
  R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
  intensity, the 3 cross-sections have the same shape 
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are
  not consistent with experiment.

@@

  When we allow monomer columns to move independently in the $z$-direction, the
  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
  diffraction patterns smooths out. We created simple systems with varying
  amounts of association between columns. In the low limit, the center of mass
  of columns are situated at the same $z$-coordinate. This is how all simple
  systems have been created up to this point. We allow increasing independence of
  columns by randomly shifting each column in the $z$-direction according to a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
  between 0 and 1. We limit this discussion to the sandwiched configuration since
  it is not feasible for columns in the parallel displaced configuration, as we
  have set them up, to move past each other. The trends seen above apply to both
  the sandwiched and parallel displaced systems. 
  %BJC9: ^need to prove that in supplemental?  
  Allowing columns to move
  independently smooths out the $q_r$ cross-section
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in
  sharp peaks. The intensity of R-$\pi$ decreases with increasing column
  independence. We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$
  versus when $f=0$. It is likely that the discrepancy between the intensity of 
  R-$\pi$ generated from our simulations versus experiment is primarily due
  to highly correlated columns in our initial configurations.

@@

>>>>

  All systems tested, although equilibrated from the perspective of the metrics used here, are
  frozen in metastable basins. Not all make physical sense or fit the experimental profile that 
  we are trying to match. In the limit of infinite simulation time, all systems will in theory 
  converge to a single equilibrium configuration, but that time is far beyond the 100's of 
  nanosecond simulated here. For simplicity, we group the systems studied here into the ordered
  and disordered basins. What we find is that any system where $\mathit{d}=3.7$ \AA~can generally 
  be characterized as being in a more ordered basin, and any system where $\mathit{d}=5.0$ \AA~can
  be characterized as a more the disordered basin. Generally, when monomers are started further 
  apart, they stay further apart than systems where monomers are started closer together 
  (see Table~\ref{table:correlation_length}). Because of the extra space between stacked 
  monomers, monomer head groups have more rotational freedom. We quantified the ordering of
  the head groups using the nematic order parameter (see section S-\ref{S-method:nematic_order}
  for details of calculation). Disordered basin systems have a lower nematic order parameter 
  (meaning they are more disordered) than ordered basin systems.

@@

  Systems built with 5 columns in each pore equilibrate to a pore spacing that
  is most consistent with the experimental value of 4.12 nm derived from SAXS
  measurements (Figure~\ref{fig:SAXS}). Ordered basin systems built with 4
  columns per pore equilibrate to an average pore spacing 0.25 nm lower than
  experiment. Ordered basin systems built with 6 columns per pore, have an
  equilibrated pore spacing ca. 0.50 nm higher than experiment.  Monomers in
  disordered basin systems built with 6 columns-per-pore agree with experimental
  pore-to-pore distances within error, but stack too far apart. Those in the
  disordered sandwiched and disordered parallel displaced configurations stack
  $\sim$~4.87 and 4.94 \AA~apart respectively, which is ca. 1.2~\AA~further apart
  than suggested by experiment. 5 column-per-pore systems stack, at a maximum,
  0.9 \AA~further apart than experiment (see 
  Table~\ref{table:correlation_length}).  The remainder of this discussion will
  focus on the analysis of systems built with 5 columns per pore.

@@

  The simulated XRD patterns of the parallel displaced configurations show additional
  weak horizontal reflections near $|q_z|= 0.7~\AA^{-1}$, half of the $q_z$ value of R-$\pi$.
  The reflection does not cross through $q_r = 0~\AA^{-1}$ so it does not necessarily appear
  for the same reason as R-double. It is possible that parallel displaced monomers contribute
  to the diffuse reflections that connect R-spots and R-double in the experimental pattern.

  %  This type of pattern is characteristic of a helix~\cite{watson_structure_1953}, as the 
  %  head groups in the parallel displaced configuration are arranged in a helix.

  We quantified the numerical discrepancies present when comparing the relative intensities
  of each reflection of interest between experimental and simulated patterns. 
  Table~\ref{table:relative_inensities_300K} shows the relative intensities of each reflection for 
  all systems tested. The patterns are normalized so that the average intensity of R-alkanes 
  must equal 1. We measured the approximate intensity of R-$\pi$ and R-double by measuring the
  intensity of the appropriate peaks of the cross-section of the 2D pattern at $q_r=0$. The 
  relative intensity of R-$\pi$ is significantly higher than experiment in our simulations. 
  R-spots is measured as the average intensity within the region bounded by a 'spot'. We 
  identified spots based on visual inspection. If the spots were not easily discernible, then the 
  intensity was taken as that of the intersection of R-alkanes at half the $q_z$ value of
  R-$\pi$, since that is where it appears experimentally. The intensity of R-spots is slightly
  lower than experiment in all cases except for the ordered basin sandwiched configuration which 
  agrees with experiment. There is no R-double intensity to be measured. Figures
  are provided in section S-\ref{S-section:xrd_intensities} to further clarify these measurements.

@@

  %To understand the most likely origin of R-spots, we determined which atoms
  %gave rise to the feature. 
  Although the monomer tails do not tilt, R-spots still originates from the 
  them. By removing all non-tail atoms from the trajectory and simulating a
  diffraction pattern with the remaining atoms, we were able to isolate the
  cause of the spots to the tails (Figure~\ref{fig:tails_rzplot}).

  %BJC9: I think Matt gets confused here. I put a more detailed explanation in 
  % the supplemental information. Do you think that's enough, or should I add
  % to this figure?
  The tails pack together hexagonally. We plotted the center of masses of the 
  first four tail atoms of each tail originating from each head group 
  (Figure \ref{fig:centroids}). We measured the angle between each center of
  mass and its nearest neighbor center of masses with respect to the $xy$ 
  plane of the membrane. We see distinct peaks in the distribution of these 
  angles located ca. $-60\degree$, $0\degree$, and $60\degree$ which is 
  consistent with a hexagonally packed configuration 
  (Figure~\ref{fig:layered_tails}). This ordering dies off at the tail ends,
  where there is more space to fill causing them to pack nearly isotropically.
  See Section~S-\ref{S-tail_packing} for a more detailed explanation of the 
  calculation and packing distributions generated from different sections of
  the tails.

@@

  The peak shape of the $q_r$ cross-section of R-$\pi$ is qualitatively different
  from experiment (Figures~\ref{fig:exp_rsection_fit} and~\ref{fig:sim_rsection_fit}).
  We use simulated XRD generated from the ordered parallel displaced configuration
  as an example in Figure~\ref{fig:rpi_exp_comparison}. The $q_z$ cross-section 
  fits a Lorentzian profile relatively well, although its full width at half maximum
  (FWHM) is 48 \% broader than the experimental cross-section 
  (Figures~\ref{fig:exp_zsection_fit} and ~\ref{fig:sim_zsection_fit}). We attempted
  to fit a Lorentzian profile to the $q_r$ cross-section and although the FWHM agrees
  with experiment within error, the fit is not optimal due to the three sharp peaks
  that appear near $q_r$ = 0.

  An exact quantitative comparison between experiment and simulation is not feasible. 
  Experimental peaks broaden due to effects that we can not easily simulate such
  as finite size crystalline domains and instrumental resolution. In our simulated
  XRD patterns, the system size imposes limitations on the resolution, which makes
  it difficult to reliably fit peaks. This is especially problematic when comparing
  the FWHM of the $q_z$ cross-section of R-$\pi$, where the experimental FWHM 
  (0.11 $\AA^{-1}$) is similar to the bin size in the $q_z$ direction (ca. 0.07 $\AA^{-1}$).
  Additionally, we model each atom with a Gaussian sphere of electron density. 
  The true electronic structure is likely much more complicated. The subsequent
  discussion primarily serves to demonstrate how we can qualitatively change the
  peak shapes to be in better agreement with experiment.

% BJC9: old version of above paragraph
%  The full width at half maximums (FWHM) of the $q_r$ and $q_z$ cross-sections
%  of R-$\pi$ are broader than experiment (Figure~\ref{fig:rpi_exp_comparison}).
%  The FWHM of the $q_z$ cross-section is 76 \% larger than experiment and the
%  $q_r$ cross-section FWHM is 21\% larger than experiment. Note that the
%  experimental data is best fit with a Lorentzian function while the simulated
%  patterns are best fit using a Gaussian function. The simulated spectra do not
%  incorporate the effects of finite domain sizes, pressure broadening and
%  instrumental broadening which would alter the peak shape. In the absence of
%  these and other peak broadening effects, the experimental peak would actually
%  be narrower, further increasing the discrepancy with simulation.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
%  There are clear qualitative differences between the experimental WAXS pattern 
%  ((a) and (c)) and the simulated XRD pattern resulting from simulations 
%  of the ordered parallel displaced configuration ((b) and (d)). 
  We compared the experimental WAXS pattern ((a) and (c)) to the simulated XRD
  pattern resulting from simulations of the ordered parallel displaced 
  configuration ((b) and (d)). The $q_r$ cross-section of R-$\pi$ ((a) and (b))
  is qualitatively different between experiment (a) and simulation (b). We fit
  Lorentzian profiles to each peak and the FWHM of the simulated pattern agrees
  with experiment within error, however the fit to the simulated data is 
  obscured by the three sharp peaks which appear near $q_r$ = 0. The $q_z$ 
  cross-sections of R-$\pi$ ((c) and (d)) are qualitatively similar. Each fits
  a Lorentzian profile well, however the FWHM of the simulated cross-section (d)
  is 48 \% larger than the experimental cross-section.}\label{fig:rpi_exp_comparison}
  \end{figure}

  We have identified a number of potential ways that simulation conditions,
  forcefield and initial configurations could affect the intensity and shape of
  R-$\pi$. We assessed each using a simplified model. Our simplified model 
  epresents each monomer head group as a single point and places them in either
  a parallel displaced or sandwiched configuration. We chose to explore the 
  influence of thermal noise in each dimension, the effect of $z$-direction 
  distance correlations between scatterers within columns, as well as correlation
  between columns since these are the variables we believe have the largest 
  influence on peak shape and intensity.

  As a baseline, we created a simplified model using the same amount of
  disorder present in our atomistic simulations. There are two sources of
  disorder to consider: thermal motion of atoms and quenched disorder which is
  created by rapid structural rearrangement during early equilibration and 
  is largely locked into place for the remainder of the simulation. The latter
  has important implications for the reproducibility of this work since both 
  initial configuration and initial velocity randomization can lead to 
  different quenched configurations. We measured thermal disorder by
  calculating the standard deviation of the distribution of head group center 
  of mass positions from their average positions. We measured quenched 
  disorder by calculating the standard deviation of the distribution of head
  group center of masses from their idealized average positions. In the 
  $z$-direction, we measured the deviation of the head group center of masses
  from an equally spaced column of head groups. In the $xy$ plane, we 
  calculated the deviation in radial position from the pore center and the
  angular deviation from equally spaced points surrounding the pore center.
  This method for calculating quenched order inherently includes thermal 
  disorder. The values measured for each system and type of disorder are given
  in Table~\ref{table:quenched_disorder}.

  The expected maximum intensity of R-$\pi$ can be calculated from a single
  trajectory of uncorrelated configurations rather than from the average of 
  multiple trajectories of correlated frames. Theoretically, in order to
  mimic the simulated system, we should build an initial configuration which 
  has the same amount of quenched disorder as our simulations and then create
  a trajectory to which we add thermal noise to each subsequent frame. In this
  scenario, the positions of each scatterer will not change in a way that 
  significantly affects the intensity of R-$\pi$ since most of its character 
  is defined by the far more disordered initial configuration. To uncover the
  expected intensity of R-$\pi$, we would need to average over many such 
  trajectories. To bypass this expensive calculation, we instead calculate the
  R-$\pi$ intensity from a trajectory consisting of many independent initial 
  configurations. This simulates the long time scales over which we expect 
  columns to sample many configurational states. %We use the latter method 
  %for the remainder of this section since we can extract the trends we 
  %need using a single trajectory at a fraction of the computational cost.

@@

  The correlation length of vertically stacked scatterers in our atomistic simulations
  are in reasonable agreement with experiment. Since it is not feasible for us to
  simulate membranes with much taller columns for increased $q_z$ resolution, and
  because the peak shape is convoluted by the extremely intense maximum of
  R-$\pi$, we measured correlation length by plotting the one-dimensional pair
  distribution function, $g(z)$, for the centers of mass of monomer phenyl rings
  (Figure~\ref{fig:correlation}). In order to calculate $g(z)$, we averaged all
  $z$-slices of the 3D correlation function within 2.1 \AA of $g(0, 0, z)$. In this
  way we are trying measure correlation between head groups within the same column.
  %We used this 
  %information to understand how far apart monomers stack within monomer columns and
  %the degree to which they are correlated.

@@

  The correlation length of the parallel displaced, ordered basin system shows
  the closest agreement with experiment (Table~\ref{table:correlation_length}).
  Note that its correlation length ($L$ = 14.5 \AA) is larger than what we would 
  expect by inverting the FWHM of the $q_z$ cross-section of R-$\pi$ shown in 
  Figure~\ref{fig:sim_zsection_fit} ($L$ = 1 / 0.163 = 6.1 \AA). The reason is
  likely a combination of artificial broadening caused by the overlap of 
  R-alkanes and R-$\pi$ as well as errors in the fit due to low simulated 
  XRD resolution. We calculated the correlation length of each system using 
  Equation~\ref{eqn:decaying_exponential}. We could not extract a reliable 
  correlation length from the disordered parallel displaced configuration since
  the peaks do not show clear patterns that can easily be fit to an exponential
  decay. The correlation length of both sandwiched systems is relatively low
  because the height of the first peak of $g(z)$ is so high.

@@

  Increased thermal noise in the $z$-direction will reduce the intensity
  of R-$\pi$, however the $q_r$ profile remains unchanged. When we increase the
  thermal noise of our simple parallel displaced system in the $z$-direction by
  12\% and 27\%, we see a 3 and 15-fold decrease in the maximum intensity of 
  R-$\pi$ respectively (Figure~\ref{fig:znoise}). Despite the decrease in 
  intensity, the 3 cross-sections have the same shape 
  (Figure~\ref{fig:rpi_xsection_vs_zsigma}, whose sharp Bragg-like peaks are
  not consistent with experiment.

@@

  When we allow monomer columns to move independently in the $z$-direction, the
  intensity of R-$\pi$ drops and the $q_r$ cross-section of the simulated
  diffraction patterns smooths out. We created simple systems with varying
  amounts of association between columns. In the low limit, the center of mass
  of columns are situated at the same $z$-coordinate. This is how all simple
  systems have been created up to this point. We allow increasing independence of
  columns by randomly shifting each column in the $z$-direction according to a uniform
  distribution bounded by (0, $f \times \mathit{d}_{equil}$) where $f$ ranges
  between 0 and 1. We limit this discussion to the sandwiched configuration since
  it is not feasible for columns in the parallel displaced configuration, as we
  have set them up, to move past each other. When $f = 1$, the columns move 
  independently and the $q_r$ cross-section smooths out 
  (Figure~\ref{fig:column_displacement}). Any amount of dependence results in sharp
  peaks. The intensity of R-$\pi$ decreases with increasing column independence.
  We see an 8-fold decrease in the intensity of R-$\pi$ when $f=1$ versus when
  $f=0$. It is likely that the discrepancy between the intensity of R-$\pi$ 
  generated from our simulations versus experiment is primarily due to highly 
  correlated columns in our initial configurations.

@@

  The columns in the simulated system are highly correlated. If the columns were
  uncorrelated, $g(z)$ of the ordered sandwiched system would very closely resemble 
  Figure~\ref{fig:z_correlation_sandwich} when we average all $z$-slices of the
  3D correlation function. When we include all $z$-slices in $g(z)$ for our system,
  the function shows oscillatory behavior and the correlation length nearly triples
  to 12.41 $\pm$ 0.69 \AA. (Figure~\ref{fig:z_correlation_fullbox}). Since all 
  columns in our initial configuration are started at the same $z$-coordinate, 
  $g(z)$ on average exhibits correlation of head groups with other head groups
  within the same column, with head groups in other columns within the same pore, 
  and with head groups in different pores.

  %BJC9: Note that the magnitude of the correlation function is much lower than 
  % in figure 10a. That's because many of the z-slices are zero when you include
  % all of them.
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{z_correlation_fullbox.png}
  \caption{When we average all $z$-slices of the 3D correlation function, the 
  correlation length of the ordered sandwich configuration nearly triples.}\label{fig:z_correlation_fullbox}
  \end{figure}
